The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-02-20 paper/ms.tex
authors, emails, keywords

\title{The impact of gas bulk rotation on the Lyman-$\alpha$ line} 
\author{
  Juan N. Garavito-Camargo\altaffilmark{1},
  Jaime E. Forero-Romero\altaffilmark{1},
  Mark Dijkstra\altaffilmark{2}
}

\altaffiltext{1}{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\altaffiltext{2}{Institute of Theoretical Astrophysics, University of Oslo, Postboks 1029, 0858 Oslo, Norway}

\begin{abstract}

@@

\begin{keywords}
{galaxies: high-redshift, galaxies: star formation, line: formation}
\end{keywords}

@@

In order to gain a deeper understanding of these results and explain
the results for the maxima in the line morphology we make 2D
histograms for the number of scatterings as a function of the outgoing
dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
such histograms in the case $\tau_{\rm H}=10^5$ for the
static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
results for the homogeneous (central) source distribution. The color
scale is logarithmic in the number of photons at a certain value
$x$-$N_{\rm scatt}$.

>>>>

\title{The impact of gas bulk rotation on the Lyman $\alpha$ line} 
\shorttitle{Rotation effects on the Lyman $\alpha$ line}
\shortauthors{Garavito-Camargo, Forero-Romero \& Dijstra}
\author{ Juan N. Garavito-Camargo and Jaime E. Forero-Romero}
\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\email{jn.garavito57@uniandes.edu.co}
\email{je.forero@uniandes.edu.co}
\author{Mark Dijkstra}
\affil{Institute of Theoretical Astrophysics, University of Oslo, Postboks 1029, 0858 Oslo, Norway}
\email{mark.dijkstra@astro.uio.no }

\keywords{galaxies: high-redshift --- line: formation --- methods: numerical ---  radiative transfer}
\begin{abstract}

@@

@@

In order to gain a deeper understanding of these results and explain
the results for the maxima in the line morphology we make 2D
histograms for the number of scatterings as a function of the outgoing
dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
such histograms in the case $\tau_{\rm H}=10^5$ for the
static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
results for the homogeneous (central) source distribution. The color
scale is logarithmic in the number of photons at a certain value
$xN_{\rm scatt}$.
